Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-06-19 paper.tex
Added prototype section in background

@@

					\noindent After edge detection, other techniques began to spread for feature extraction. 
					In a paper by Kumar and Kumar Bhatia written in 2014 \cite{kumar2014detailed}, 
					there are some examples of techniques used to extract features. 
					In the first one, the authors present different types of features and then some techniques to extract them. 
					These are:

@@

						\item \textbf{Chain Code Histogram of Character Contour}:

							This method is based on a contour following technique. 
							The contour following uses a chain coding standard proposed by Freeman, that assigns a value to every pixel to identify the next pixel in the border.

						\item \textbf{Finding Intersection/Junction in character}:

							Using the same standard proposed by Freeman used in Chain Code Histogram, there is the possibility to count intersections (or junctions) and open ends in a figure.

						\item \textbf{Transition feature}:

							This method is based on the transition from background to foreground. 
							There are different techniques that can work both on gray level images or in 4-connected or 8-connected images.

@@

				\noindent These were not the only techniques presented in the paper, but since some were more problem-specific (about handwritten character recognition)
				were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
				The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
				Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
				In another paper, written in 2013 by Tian \cite{ping2013review}, there are some other techniques cited that may result useful:

@@

					\item \textbf{colour features}:

						colour is one of the most important features humans can perceive. 
						The features we can extract depend on the colour space, but once it is defined there are some possibilities. 
						A few examples are colour histograms, colour moments and colour coherence vectors. 
						One of the simple and meaningful, according to the authors, is colour moments. 
						The most common colour moments are the mean, the standard deviation and the skewness.

@@

				\begin{figure}[!ht]
					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
					\caption{Color histogram of the image used in \ref{fig:1}}
					\label{fig:2}
				\end{figure}

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since, depending on the formulation of the energy function, the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. 
					For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
					simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
					update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
					The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
					energy cost, which corresponds to the best template match.

@@

					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
					In 2019, Halimi et al. wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{halimi2019unsupervised}. Although this paper examines the techniques for 
					3D shapes, it is very likely that it can be adapted to extract 2D features from images.\\
					The background of this experiments is formed of some concepts that are not immediate. One of the concepts used as background is the minimum distortion correspondence. The other are, for example, 
					descriptor learning, functional maps and deep functional maps. These concepts serve as a base for all the work done later. \\
					In particular, the authors focus on unsupervised deep functional maps. The authors state that the main contribution of their paper is that they introduce a technique with which they can 
					avoid annotating a lot of data before training a model. After reducing the number of vertices to a number between 5000 and 7000, the authors used a deep functional map network. The inputs are 
					fed to two residual neural networks, which compute a dense descriptor fields. These descriptors, are the inputs to the functional map layer. Lastly, as post processing, a point-wise map recovery was 
					applied and, after that, the shape was upscaled to the original resolution.

					\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{varshni2019pneumonia}. This paper has the objective to classify images using CNNs to understand if a patient 
					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it is reported that the best model architecture is DenseNet-169. This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing. The model used in 
					particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.

>>>>

		\subsection{Prototypes}

			\noindent Prototypes are another key concept used in this paper and, as the concept of typicality, should be defined. In this case, there are some differences based on the field that it is 
			examined. According to Murphy's Big Book of Concepts\cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
			it is specified that this item may not be something that exists physically, but it is an average of what people see from real world examples. Adopting the example that the 
			author uses in the book, which is about dogs, ``just your abstraction of what dogs are most often like''. This opens the possibility to the fact that every person has, for the 
			same category, a different prototype. That is why, in this paper, the prototypes will be treated as an average, among different people, of the examples weighted with the 
			average perceived typicality.\\
			Although this is the concept of prototype that will be used in this paper, there are numerous different possibilities. For example, could be intended in a software-engineering way 
			as the first example of a new product, or in a HCI-like way as a representation of conceptual design as stated by Prof. Narges Mahyar of the University of 
			Massachusetts \cite{hciprot}. Another example is the concept of prototype used by Smith et al. in an article, in which they stated that a prototype is ``a prestored representation 
			of the usual properties associated with the concept's instances'' \cite{smith1988combining}. This view in some way generalizes the definition expressed by Murphy in his book. \\
			For the goal of this paper, the best way to define a prototype is the one used by Murphy, although with a small modification to take into account also the typicality of every 
			example to create the prototype. Also Smith's way to define a prototype would be interesting to use, but since Murphy's way is a bit more specific, it is probably easier to use.

@@

					\noindent After edge detection, other techniques began to spread for feature extraction. 
					In a paper by Kumar and Kumar Bhatia written in 2014 \cite{kumar2014detailed}, 
					there are some examples of techniques used to extract features. 
					In this paper, the authors present different types of features and then some techniques to extract them. 
					Some of the most important are:

@@

@@

				\noindent These were not the only techniques presented in the paper, but since some were more problem-specific (about handwritten character recognition)
				were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
				The techniques were: Fractal theory techniques, Chain Code Histogram of Character Contour, Finding Intersection/Junction in character, 
				Shadow features of character, Sector approach for feature extraction, Transition feature
				Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
				In another paper, written in 2013 by Tian \cite{ping2013review}, there are some other techniques cited that may result useful:

@@

					\item \textbf{Colour features}:

						Colour is one of the most important features humans can perceive. 
						The features we can extract depend on the colour space, but once it is defined there are some possibilities. 
						A few examples are colour histograms, colour moments and colour coherence vectors. 
						One of the simple and meaningful, according to the authors, is colour moments. 
						The most common colour moments are the mean, the standard deviation and the skewness.

@@

				\begin{figure}[!ht]
					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
					\caption{Color histogram of the image used in Figure \ref{fig:1}}
					\label{fig:2}
				\end{figure}

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since, depending on the formulation of the energy function, the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.

@@

					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
					\noindent In 2019, a paper written by Varshni et al. that proposes a method~\cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
					has pneumonia or not. After the preprocessing, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it is reported that the best model architecture is DenseNet-169.
